---
title: "R_review"
author: "meizheng"
date: "2019年5月13日"
output: html_document
---

###1.R的基本介紹

 **基本運算**

* 次方**"^"**

* 求餘數**"%%"**

* 求商數**"%/%"**

*範例*
```{r}
3^4  #次方
31%%7  #餘數
31%/%7  #商數
```

**函數使用**

* **mean()** 平均

* **var()** 變異數

*範例*
```{r}
c <- 1:11
mean(c)
var(c)
```

**向量**

* **c()** 將各種數字或字串集合成向量

*  **joint()**

* 向量運算

*範例*
```{r}
c(0,7,8) #c() is used collect things together into vector
x <- c(0,7,8)
numbers5to20 <- 5:20
joint <- c(numbers5to20,x) #joint together
joint[5] #呼叫向量中第五個位置的數
joint[c(1,3,5,7)] #呼叫多個位置的數
x[-2] #select all but the second element of x
x*3 #向量內每個數皆*3
x-5 #向量內每個數皆-5
x^3
```


**向量相關函數使用**

* **seq()** 連續數字 如果要有間隔(隔2,3,...) 函數內令 by=

* **rep()** 重複數字或向量

*範例*
```{r}
seq(1,21,by=2) 
rep(3,12) #3重複12次
rep(c(1,4),c(3,2)) #1重複3次;4重複2次
rep(c(1,4),each=3)
rep(seq(2,20,2),rep(2,10)) #每個值重複2次
```

* **substr(x,n,m)** x:某個向量 n,m:向量內每個元素從位置n取到m

* **paste()** 在向量內的每個元素黏上額外的東西

*範例*
```{r}
colors <- c("red","yellow","blue")
more.colors <- c(colors,"green","magenta","cyan")
substr(colors,1,2)
paste(colors,"flowers")
paste("several",colors,"s",sep=" ")
paste("I like",colors,collapse=",")
```

**factor()**

```{r}
grp <- c("cat","dog","cat","dog")
grp <- factor(grp)
grp
as.integer(grp)
levels(grp)
levels(grp)[as.integer(grp)]
```

**matrix and arrays**

* **matrix()**

*範例*
```{r}
m <- matrix(1:6,nrow=2,ncol=3)
m
m[1,2] #第一列第二行
m[1,] #第一列
m[,1] #第一行
a <- array(1:24,c(3,4,2))
a
```

* **dataframe()**

*範例*
```{r}
colors <- c("red","yellow","blue")
numbers <- c(1,2,3)
colors.and.numbers <- data.frame(colors,numbers,more.numbers=c(4,5,6))
colors.and.numbers
```

##2.Built-in functions and online help
q() is an example of a **built-in function**.There an many functions in R which are designed to do all sorts of things.The **online help** facility can help you to see what a particular function is supposed to do.

**know the name of the function**

```{r}
#?mean
#help(mean)
```

* **built-in graphics functions**

```{r}
x <- c(12,15,13,20,14,16,10,8,15)
hist(x)
```

##Programming statistical graphics

* bar chart

```{r}
VADeaths
barplot(VADeaths,beside=TRUE,legend=TRUE,ylim=c(0,90),ylab="Deaths per 1000",main="Death rates in Virginia")
```

* dot chart

```{r}
dotchart(VADeaths,xlim=c(0,75),lab="Deaths per 1000",main="Death rates in Virginia")
```

* histograms

```{r}
x <- rnorm(100)
hist(x)
```

* boxplot

```{r}
boxplot(Sepal.Length ~ Species,data=iris,ylab="Sepal length (cm)",main="Iris measurements",boxwex=0.5)
```

* Scatterplots

```{r}
x <- rnorm(100)
y <- rpois(100,30)
plot(x,y,main="Poisson versus Normal")
plot(x,y,type="l")
plot(sort(x),sort(y),type="l")
```

* QQplots
```{r}
X <- rnorm(1000)
A <- rnorm(1000)
qqplot(X,A,main="A and X are the same")
B <- rnorm(1000,mean=3,sd=2)
qqplot(X,B,main="B is rescaled X")
C <- rt(1000,df=2)
qqplot(X,C,main="C has heavier tails")
D <- exp(rnorm(1000))
qqplot(X,D,main="D is skewed to the right")
```

* adding to plots

```{r}
#先創個dataframe
sex <- c("M","F","M","F","F","M","F","M")
length <- c(7.9,6.5,8.4,5.5,6.5,8.0,7.0,7.5)
width <- c(2.3,1.7,2.6,1.7,1.9,2.1,1.8,1.9)
indexfinger <- data.frame(sex,length,width)
plot(width~length,data=indexfinger)
#lighlight the longest male and female
with(indexfinger[c(3,7),],points(length,width,pch=15))
#add linear regression for males
abline(lm(width~length,data=indexfinger,subset=sex=="M"),lty=1)
#add linear regression for females
abline(lm(width~length,data=indexfinger,subset=sex=="F"),lty=2)
#add legend for two lines
legend("topleft",legend=c("Male","Female"),lty=1:2)

```

* annotate graphs outside the plot region

```{r}
par(mar=c(5,5,5,5)
    +0.1)
plot(c(1,9),c(0,50),type="n",xlab="",ylab="")
text(6,40,"Plot region")
points(6,20)
text(6,20,"(6,20)",adj=c(0.5,2))
mtext(paste("Margin",1:4),side=1:4,line=3)
mtext(paste("Line",0:4),side=1,line=0:4,,at=3,cex=0.6)
mtext(paste("Line",0:4),side=2,line=0:4,,at=15,cex=0.6)
mtext(paste("Line",0:4),side=3,line=0:4,,at=3,cex=0.6)
mtext(paste("Line",0:4),side=4,line=0:4,,at=15,cex=0.6)
```

##Programming with R##

* for迴圈

```{r}
Fibonacci <- numeric(12)
Fibonacci[1] <- Fibonacci[2] <-1
for (i in 3:12) Fibonacci[i] <- Fibonacci[i-2]+Fibonacci[i-1]
```

* if()

```{r}
corplot <- function(x,y,plotit){
  if (plotit == TRUE)
    plot(x,y)
  cor(x,y)
}
corplot(c(2,5,7),c(5,6,8),FALSE)
```

* **repeat** loop and the **break** and **next** statements

```{r}
x <- 3
tolerance <- 0.000001
repeat {
  f <- x^3+2*x^2-7
  if (abs(f)<tolerance) break
  f.prime <- 3*x^2+4*x
  x <- x-f/f.prime
}
x
```

##Simulation##

```{r}
random.number <- numeric(50)
random.seed <- 27218
for (j in 1:50){
  random.seed <- (171*random.seed) %% 30269
  random.number[j] <- random.seed/30269
}
random.number
```

* uniform隨機變數

```{r}
set.seed(32789)#ensures that output will match others
runif(10,min=-3,max=-1)
```

* bernoulli 隨機變數

```{r}
set.seed(23207)
guesses <- runif(20)
correct.answers <- (guesses <0.2)
correct.answers
table(correct.answers)
```

* binomial 隨機變數

```{r}
#probability of getting four heads in six tosses of a fair coin
dbinom(x=4,size=6,prob=0.5)
#cumulative probability(P(X<=4))
pbinom(4,6,0.5)
#the quantiles for the binomial distribution(89th percentile)
qbinom(0.89,6,0.5)
```

* poisson

```{r}
dpois(x=3,0.5)
rpois(10,3.7)
```

##Computatinal linear algebra##

```{r}
H3 <- matrix(c(1,1/2,1/3,1/2,1/3,1/4,1/3,1/4,1/5),nrow=3)
H3
1/cbind(seq(2,4),seq(2,4),seq(3,5))
1/rbind(seq(2,4),seq(2,4),seq(3,5))

matrix(seq(1,12),nrow=3)
x1 <- seq(1,3)
x2 <- x1^2
X <- cbind(x1,x2)
X
X[3,2]
X[3,]
X[,2]
#if we want to maintain the result as a row or column vector ,use drop=FALSE
X[3,,drop=FALSE]
X[,2,drop=FALSE]
colnames(X)
rownames(X)
#assign names
rownames(X) <- c("obs1","obs2","obs3")
X
```

* matrix properties

```{r}
dim(X)
diag(X)
```

